Multiproduct Batch Processing Time Maximization Problem

### 2023-06-26 (2023) Fraga et al.tex
updating paper
writing introduction - before Regi's contribution

The scientific literature presents several papers that address the multi-product batch problem. Most works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine production ordering and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}. In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed. The solution must be determined in such a way that both setup and storage costs are minimized. Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}. Other important works deal with the design of a multi-product batch plant. In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the
equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.

@@

@@

\section{Mathematical model}
\label{}

@@

\section{Analytical solution}
\label{}

@@

\section{Tests and results}
\label{}

@@

\section{Contributions}

@@

@@

\bibitem[\protect\citeauthoryear{Liu et al}{2020}]{LiuEtAl2020}
Liu, G., Li, F., Yang, X., and Qiu. S. (2020). The multi-stage multi-product batch-sizing problem in the steel industry. {\it  Applied Mathematics and Computation}, Vol. 369, 124830.

\bibitem[\protect\citeauthoryear{Omega}{1993}]{Omega1993}
OMEGA Journal. (1993). Single Machine Multi-product Batch Scheduling: Testing Several Solution Methods. {\it  OMEGA Int. J. of Mgmt Sci.}, Vol. 21 (6), pp. 709--711.

>>>>

The scientific literature presents several papers that address the multi-product batch problem. Many works target the problem of multi-product batch scheduling (MPBS), in which it is necessary to determine production ordering and the ideal batch size for each product, in a production of several products which share the same production facilities and for which demand is known \citep{Eilon1985}. In this problem, a single product is processed at a time, so it is necessary that the quantity produced is sufficient to meet the demand during the period in which other products are being processed. The solution must be determined in such a way that both setup and storage costs are minimized. Among the authors who addressed this problem are \cite{Eilon1985}, \cite{Omega1993} and \cite{LiuEtAl2020}. In the papers mentioned above, production in a single unit or in a  simple serial flowshop plant is considered, in which all products follow the same linear flow through the production units. \cite{KimEtAl1996} consider the multi-product batch problem in networked processes. As defined by the authors, in this case, the production units are not arranged in a line, and the connection between the units may or may not exist. Therefore, the production paths in the flowshop network can be different for each product. Also the passing of previous batch can be possible so that the final sequence of the production at the last stage units can be different from the initial sequence. Other important works deal with the design of a multi-product batch plant. In this case the problem is to obtain the configuration of the plant and the equipment that minimize the capital cost of all the equipment items needed to fulfill the production requirements \citep{RavemarkAndRippin1998}.

@@

In the next sections, a presentation of the multi-product batch processing time maximization problem is made, along with an application example. Section \ref{sec:mathModel} presents an interger linear mathematical model for the problem and section \ref{sec:analyticalSol} presents an analytical method for its solution. Section \ref{sec:results} presents the tests and results obtained by a solver in C++ applying the analytical solution and a solver developed in LINGO to new proposed benchmarks. In sections \ref{sec:contributions} and \ref{sec:acknowledgments}, the contributions of this work are informed and acknowledgments are given, respectively. Finally, section \ref{sec:conclusions} presents the paper's conclusions and suggestions for future works.

@@

\section{Mathematical model}
\label{sec:mathModel}

@@

\section{Analytical solution}
\label{sec:analyticalSol}

@@

\section{Tests and results}
\label{sec:results}

@@

\section{Contributions}
\label{sec:contributions}

@@

\section{Acknowledgments}
\label{sec:acknowledgments}

\section{Conclusions and suggestions for future works}
\label{sec:conclusions}

@@

\bibitem[\protect\citeauthoryear{Kim \emph{et al.}}{1996}]{KimEtAl1996}
Kim, M., Jung, J. H. and Lee, I. (1996). Intelligent scheduling and monitoring for multi-product networked batch processes. {\it  Computers chem. Engn}, Vol. 20 (Suppl.), pp. 1149--1154.

\bibitem[\protect\citeauthoryear{Liu \emph{et al.}}{2020}]{LiuEtAl2020}
Liu, G., Li, F., Yang, X., and Qiu. S. (2020). The multi-stage multi-product batch-sizing problem in the steel industry. {\it  Applied Mathematics and Computation}, Vol. 369, 124830.

\bibitem[\protect\citeauthoryear{Omega Journal}{1993}]{Omega1993}
OMEGA Journal. (1993). Single Machine Multi-product Batch Scheduling: Testing Several Solution Methods. {\it  OMEGA Int. J. of Mgmt Sci.}, Vol. 21 (6), pp. 709--711.
